\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{PS5_Beake}
\author{Dillon Beake}

\begin{document}
\maketitle

\section{Web Scraping - no API}

I was able to collect an NFL players combine/draft measurements using Wikipedia.  
\subsection{}
I found this useful because I was able to find an NFL player and his corresponding athletic key performance indicators, e.g. 40 yd dash, and broad-jump.  I was able to collect anthropomorphic measurements e.g. arm length, height. 
\subsection{}
further, I was able to parse this information into a table of easy to read columns and rows. 
\subsection{}
I found this useful because I'd like to look at some of these measurements and make some possible predictions about physical development.  
\subsection{}
I used class examples and Chatgpt to parse the data

\section{API}
Finding API end documents for the NFL combine results proved to be rather difficult. 
I was finally able to locate, and register for an API key, through a website that had many NFL packages to choose from.  However, did not have anything speecifically for the draft results.   
\subsection{}
I did collect Data on NFL Players from every roster in the NFL.  The data was interesting it included, Name, Team, Uniform number, Height, Weight, and even their individual photos you would find on their team websites.  
\subsection{}
The data was interesting.  Using an API-key,and API end documents in R was also very interesting.   However, I'd like to find more player measurement data.  The problem is that sites like NFL.com and Espn.com do not allow the use of API keys.  So I will need to keep searching.  
\subsection{}
The package I used was found Sportsdata.io. 


\

\end{document}